\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-28 paper.tex
Update paper.tex

%\usepackage[T1]{fontenc}
%\usepackage{mathptmx}
\soulregister\cite7
\soulregister\ref7
\pagestyle{plain}

@@

\begin{abstract}
Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space. 
Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to fully recover failure disks. 
However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.

Therefore, we propose Approximate Codes for video data, which significantly reduce storage overhead and increase availability for more important data segments.
Approximate Codes provide complete recovery when fewer disks fail, and approximate recovery (recover most data) in the event of multiple disk failures.
To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
The results show that compared with the typical high-reliability erasure code schemes, Approximate Codes reduce the storage overhead by 7.64\% at the expense of reasonable probability of video quality loss.

@@

Existing erasure codes are designed to completely recover corrupted data. Typical configurations use triple disk failure tolerant arrays (3DFTS), such as Windows Azure [], which requires at least 3 parity disks. These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of video applications can tolerate a certain amount of data loss. For example, video data typically records at least 20 frames per second, which makes losing a few frames difficult for a typical user to perceive. In addition, even if the video data suffers a certain loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].

@@

Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application. For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to. Therefore, the encoded video data has an uneven degree of importance, that is, it is tolerable that some of those less important data losses because the users are hard to detect. On the other hand, loss of important data will have more serious consequences.

@@

\subsection{Approximate Storage}
Approximate Storage loosen the requirement of storage reliability by allowing some quality loss of specific data, which recently receives more attentions since data centers are trading off the limited resource budget with the costly reliability requirements of ever-increasing data.

\subsection{Video Storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage. Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.

@@

@@

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data. In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
\label{apcode-7222-v2}
\end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\soulregister\cite7
\soulregister\ref7
\pagestyle{plain}

@@

\begin{abstract}
Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to equally back up all data.
However, this is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to the ignorance of redundant information inside the data, which results in multiple complete parity disks being excessive.

Therefore, we propose Approximate Codes for video data, which significantly reduce storage overhead and increase availability for more important data segments.
Approximate Codes provide complete recovery when fewer disks fail, and ensure approximate recovery (recover most data) in the event of multiple disk failures.
To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
The results show that compared with the typical high-reliability erasure code schemes, Approximate Codes reduce the storage overhead by 7.64\% at the expense of reasonable probability of video quality loss.

@@

Existing erasure codes are designed to completely recover corrupted data. Typical configurations use triple disk failure tolerant arrays (3DFTS), such as Windows Azure [], which requires at least 3 parity disks. These methods are often excessive because scenes with 3 disks being corrupted at the same time are very rare as well as they do not consider that plenty of video applications can tolerate a certain amount of data loss. For example, video data typically records at least 20 frames per second, which makes losing a few frames difficult for a typical user to perceive. In addition, even if the video data suffers a certain amount of loss, the existing AI-based interpolation algorithm and super pixel algorithm can recover most of the damaged data [].

@@

Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application. For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to. Therefore, the encoded video data has an uneven degree of importance, that is, the loss of some less important data is tolerable because it's hard for human eyes to detect. On the other hand, loss of important data will have more serious consequences.

@@

\subsection{Video Storage}\label{video storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage. Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}

@@

\subsection{Approximate Storage}
Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

It loosens the requirement of storage reliability by allowing some quality loss of specific data. Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks. The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices. Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.

However, it is too naive to store data in approximate storage units indiscriminately. Related research [] shows that this can lead to unacceptable data pollution. To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.

In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP. An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable. In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.

\subsection{Video Frame Recovery: Frame Interpolation}
In the circumstance of data loss, it's common to lose some frames and then the video is not complete. One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates. Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.

Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames. This is a technique that can model natural motion within a video, and generate frames according to this modelling. Artificially increasing the frame-rate of videos enables the possibility of frame recovery. Optical flow is commonly addressed in the video frame interpolation problem. Optical flow is the pattern of apparent motion of objects, surfaces, and edges in a visual scene caused by the relative motion between an observer and a scene. Video frame interpolation algorithms typically estimate optical flow or its variations and use them to warp and blend original frames to produce interpolation results.

Recently, phase-based methods have shown promising results in applications such as motion and view extrapolation \cite{didyk2013joint}\cite{wadhwa2013phase}\cite{meyer2015phase}. These methods rely on the assumption that small motions can be encoded in the phase shift of an individual pixel¡¯s color. Meanwhile, deep learning approaches, and in particular Convolutional Neural Networks (CNNs), have set up new state-of-the-art results across many computer vision problems which also makes big improvements to frame interpolation. In neural networks, optical flow features are trained in a supervised setup mapping two frames to their ground truth optical flow field\cite{dosovitskiy2015flownet}\cite{ilg2017flownet}. Among them, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the best results in terms of PSNR and middlebury benchmark respectively.

All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle). However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames. Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.

@@

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
Figure \ref{apcode-7222-v4} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v4.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data. In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
\label{apcode-7222-v4}
\end{figure}
